Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-05-23 abstract.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

We study the quantum quench problem for a class of bosonic conformal interface by computing the fidelity and Loschmidt echo. The scattering matrix $S(\theta)$ associated with the permeable interfaces are classified into two sectors of $O(2)$ group. The fidelity and Loschmidt echo decay algebraically as $t^{-\alpha}$ after the quench. The exponent $\alpha$ is found to depend on the change of $\theta$ as a quadratic relation if the boundary conditions (before and after quench) are in the same sectors of $O(2)$, while remain $\frac{1}{4}$ if they belong to different sectors. We confirm our results by various numerical simulations. The winding modes of compact bosons will have no contribution at leading order. We expect such conformal interface can be realized in a wide range of experiments of one-dimensional bosonized electron gas.

%1. cut and joint two different CFT

%7 Experiment

>>>>

We study the quantum quench problem for a class of bosonic conformal interface by computing the Loschmidt echo and the bipartite fidelity. These boson conformal interfaces can be viewed as the change of boundary conditions (quench) when connecting two one-dimensional critical systems. They are classified by $S(\theta)$ matrices associated with the current scattering processes on the interface. The resulting Loschmidt echo of the quench has long time algebraic decay $t^{-\alpha}$, whose exponent also appears in the finite size bipartitle fidelity as $L^{-\frac{\alpha}{2}}$. We perform analytic and numerical calculation of the exponent $\alpha$, and find that it has a quadratic dependence on the change of $\theta$ if the prior and post quench boundary conditions are in the same type of $S$, while remains $\frac{1}{4}$ otherwise. Possible physical realizations of these interfaces includes for instance connecting different quantum wires (Luttinger liquids), quench of the topological phase edge states \etc and the exponent can be detected in a X-ray edge singularity type experiment.

%%% Local Variables:
%%% TeX-master: "bCFT_paper"
%%% TeX-PDF-mode: t
%%% End:

### 2017-05-23 analy_eval.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

In this subsection, we relate the free energy to the amplitudes between boundary states and give analytic results.

@@

We thus add small semi-circles around the points where the bcc operators reside, followed a series of conformal mapping. For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
\end{equation}

The Loschmidt echo can be evaluated the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law increase of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence 
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta 
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.

>>>>

In this subsection, we relate the free energy to the amplitudes between boundary states and present the analytic results.

@@

We thus add small semi-circles around the points where the bcc operators reside, followed by a series of conformal mapping. For the fidelity case, the regulators as well as conformal mapping are depicted in Fig.~\ref{fig:fidel-map}. 
\begin{figure}[h]
\centering
\includegraphics[width=\columnwidth]{fig_fidel-map.pdf}
\caption{Mapping from a strip to the upper half plane $w = \frac{L}{\pi} \ln z $. The two black dots represent possible insertion of bcc operators. The dot inside the blue semi-circle is at coordinate $z = 1$, which is the image of point connecting $a$ and $b$ boundaries. The other dot is at $z = 0$, and corresponds to the connection between $a$ and $c$ boundaries at $- \infty$. To evaluate the diagram, we add the outer-semi-circle as the IR cut-off, it can also be regarded as the image of the blue vertical line on the $w$ plane.}
\label{fig:fidel-map}
\end{figure}
We assume $a = c$ such that there is only one bcc operator on the real axis enclosed by the regulator. The two end points of the $\epsilon$ radius semi-circle on the $w$ plane are mapped to
\begin{equation}
\exp( \pm \pi \frac{\epsilon}{ L}  ) \sim 1 \pm \pi \frac{\epsilon}{L} 
\end{equation}
The vertical line at $\text{Re} w = W$ (IR regulator) is mapped to $|z| = e^{\pi \frac{W}{L} } \gg 1 $. Since the radius of this larger circle is overwhelming, moving the inner semi-circle on the $z$ plane to the center will not affect the cross ratio to the leading order. The dashed line and solid line can then be regarded as two boundary states, the diagram corresponds to the following partition function is 
\begin{equation}
  Z_{ab} = \langle a | e^{-\pi H } |b \rangle 
\end{equation}

The Loschmidt echo can be evaluated the same way. Again we introduce two semi-circles (blue in Fig.~\ref{fig:H-tau_fold}) as regulator and then perform the conformal transformation shown in Fig.~\ref{fig:H-tau_fold}. In the $\xi$ plane, we end up with the same diagram as fidelity. With one more conformal mapping, it is becomes the cylinder partition function between two boundary states.

@@

The results of the general partition function $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and its free energy are evaluated in App.~\ref{app:lambda_12} to the leading order of cylinder width $\beta$. But one can't use these results na\"ively as we have tacitly introduced shifts in doing these conformal transformation. In fact, directly using the free energy given in App.~\ref{app:lambda_12} resulting in a power law surge of Loschmidt echo, which does not agree with the known results. One easy way to see the shift is that free energy is zero when $a,b,c$ are all periodic boundary conditions, hence there is a necessary shift
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta 
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection is performed in App.~\ref{app:F_correction}, where the correction is found to be coming from the Schwartzian and outer circle regulator.

### 2017-05-23 bCFT_paper.tex
bCFT_paper restored, intro wasn't there but added manually. All the standalone figures are there, most likely
Merge branch 'master' of https://bitbucket.org/msgboxa/bcft_paper (reverted from commit 5385d6b0de3258810667564c8e0a53e008f8f561)
[draft] discussion restored.
[draft] add boson bogoliubov transformation original tex file
1. Hamiltonian changed to A B notation 2. bmatrix, pmatrix used 3. \tilde{S} changed to \mathcal{S} 4. labeling changed
[draft] App. A draft finished.
[draft] 1. compact boson moved to appendix 2. added compact_boson but just started 3. general formulation nearly finis

\documentclass[preprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[font={footnotesize}]{caption}
\usepackage{todonotes}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}

\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

@@

\begin{abstract}
\end{abstract}

@@

\section{Introduction}
% the last one to be finished.

\section{Bosonic Conformal Interface}
\subsection{General Formulation}
% M, S
% special case
\subsection{Physical Realization: Connecting Bosons of Different Compactification Radii}
% free boson + compact
\subsection{A Free Boson Lattice Model}
% cite Calabrese, introduce the model
% lattice model S matrix

\section{Bipartite Fidelity and Loschmidt Echo}
\subsection{Definition}
% definition
% general discussion

\section{Analytic and Numerical Results}
\subsection{Fidelity}
% analytic: conformal transformation
% numerical comparison 
\subsection{Loschmidt Echo}
% analytic: conformal transformation
% numerical comparison

\section{Discussion}

\begin{acknowledgments}
\todo[inline]{Thomas Faulkner, Xueda Wen, Shinsei Ryu, Romain Vasseur}
    TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
    This work made use of the Illinois Campus Cluster, a computing resource that is operated by the
    Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for
    Supercomputing Applications (NCSA) and which is supported by funds from the University of
    Illinois at Urbana-Champaign.
\end{acknowledgments}

\appendix
\section{Corrections to the Free Energy}
% two corrections:
% 1. staircase geometry
% 2. contribution from the boundary: cite Cardy

\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
% basis transformation, Bogoliubov state, overlap(master theorem)
% Peschel_EE.pdf

\section{A Determinant Identity for the Boundary State Amplitude}
% copy notes app. C

\section{$\lambda_1 \rightarrow \lambda_2$ Boundary State Amplitude}
% copy notes app. B

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
% copy notes app. A

>>>>

\documentclass[reprint, prb]{revtex4-1}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{enumitem}
\usepackage{bm}
\usepackage[caption=false]{subfig}
\usepackage{todonotes}
\usepackage{comment}
\graphicspath{{./}{./images/}}
\definecolor{darkblue}{rgb}{0.1,0.2,0.6} \definecolor{darkred}{rgb}{0.8,0.1,0.2}
\usepackage[colorlinks,citecolor=darkblue,linkcolor=darkred,urlcolor=darkblue]{hyperref}
\usepackage[all]{hypcap}
\renewcommand{\vec}[1]{\boldsymbol{\mathbf{#1}}}

@@

\begin{abstract}
\input{abstract}
\end{abstract}

@@

\section{Introduction}
\input{intro}

\section{Bosonic Conformal Interface}
\label{sec:bosonic_conformal_interface}
\subsection{General Formulation}
\label{sec_sub:general_formulation}
\input{general_formulation}
\subsection{A Free Boson Lattice Model}
\label{sec_sub:free_boson_lattice}
\input{free_boson_lattice}

\section{Bipartite Fidelity and Loschmidt Echo}
\label{sec:analytic_numerics}
\subsection{Definition}
\input{def_fidel_echo}
\subsection{Notation of Boundary Conditions}
\label{sec:notation}
\input{bd_notation}
\subsection{Analytic Evaluation}
\label{sec_sub:analy_eval}
\input{analy_eval}
\subsection{Numerical Results and Comparison}
\input{num_result}

\section{Discussion}
\label{sec:disc}
\input{disc}

\section{Conclusion}
\label{sec:conclusion}
\input{conclusion}

\begin{acknowledgments}
\todo[inline]{Mao: funding number?}
We are grateful for the discussion and suggestions provided by Thomas Faulkner, Xueda Wen, Shinsei Ryu, Taylor Hughes and Romain Vasseur during the course of this research. 
TZ is supported by the National Science Foundation under grant number NSF-DMR-1306011.
This work made use of the Illinois Campus Cluster, a computing resource that is operated by the Illinois Campus Cluster Program (ICCP) in conjunction with the National Center for Supercomputing Applications (NCSA) and which is supported by funds from the University of Illinois at Urbana-Champaign.
\end{acknowledgments}

\appendix
\section{Corrections to the Free Energy}
% two corrections:
% 1. staircase geometry
% 2. contribution from the boundary: cite Cardy 
\label{app:F_correction}
\input{F_correction}

\section{Conformal Interface in Free Bosonic Lattice}
\label{app:interface_free_boson}
\input{interface_free_boson}

\section{Numerical Computation of Bipartite Fidelity and Loschmidt Echo}
% basis transformation, Bogoliubov state, overlap(master theorem)
% Peschel_EE.pdf
\label{app:comp_fid_echo}
\input{comp_fid_echo}

\section{A Determinant Identity for the Boundary State Amplitude}
\label{app:pf_of_id}
% copy notes app. C
\input{pf_of_id}

\section{Alternative Approach to ${\rm DN} \rightarrow \lambda$ Amplitude}
\label{app:gnd_dn_lambda}
% copy notes app. A
\input{gnd_dn_lambda}

\section{General Boundary State Amplitude}
\label{app:lambda_12}
% copy notes app. B
\input{lambda_1_lambda_2}

\section{Winding Modes of Compact Bosons}
% free boson + compact
\label{app:compact_diff_boson}
\input{compact_boson}

### 2017-05-23 bd_notation.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) 
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we usually take $a = c$ in the numerical calculation.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} 
\end{equation}
The scaling dimension of this bcc operator does indeed deviate from the completely transmitting case for certain choice of boundary conditions.

Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

>>>>

We use chemical reaction style to represent the change of boundary conditions. Taking the example of the echo diagrams in Fig.~\ref{fig:echo}, there are three boundary conditions $a,b,c$ in the folding picture, which represents the status on two ends of the chain before and after the quench. The choice of a uniform $c$ boundary condition on the far end of the chain is to isolate the effect coming from the bcc on the conformal interface. The process $a + c \rightarrow b + c$ represents the change of boundary condition from the combination $a$/$c$ on the two ends to $b$/ $c$ after the quench. Since each letter can take a general conformal interface defined by the $S$ matrix in Eq.~\eqref{eq:S1_S2}, we denote it as
\begin{equation}
S_a( \theta_a ) + S_c( \theta_c) \rightarrow S_b( \theta_b )  + S_c( \theta_c ) 
\end{equation}
Analytic computation can be performed when we neglect the boundary condition $c$, assuming $L \gg \tau$. To remove the bcc operator from $c$ to $a$ at infinity, we take $a = c$ in the numerical calculation.

In the ``cut-and-join" protocol we considered, $a$ should be one of `DD', `DN', `ND', `NN', $b$ is taken to be $S_1( \theta )$ or $S_2( \theta )$. The physical situation of connecting two compact bosons and our lattice model corresponds to the choice of $S_1( \theta)$, we also reserve the notation $\lambda$ for this type of boundary condition. For instance, the notation for the process presented in Fig.~\ref{fig:echo} is
\begin{equation}
{\rm DN }  + {\rm DN} \rightarrow \lambda + { \rm DN} 
\end{equation}
Another interesting case is to take $a$ or $c$ to be completely transmitting interface, i.e. $S_2( \frac{\pi}{4} )$. This corresponds to the traditional periodic boundary condition and we use symbol 'P' to denote it.

### 2017-05-23 compact_boson.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

\subsection{Gluing Condition for Winding Modes}
\label{app_sub:compact_gluing_boundary}

Following the treatment of boundary CFT in Ref.~\onlinecite{di_francesco_conformal_1997}, we shall quantize the theory by imposing \emph{equal-time} commutator for $a_n$ and $\bar{a}_n$ in Eq.~\eqref{eq:boson-mode-exp}. The conformal boundary state will be defined on a constant time slice, say $t=0$. For the permeable wall connecting two compactified bosons, this results in folding $t\rightarrow-t$ rather than $x\rightarrow-x$ as in the main text. Since the two cases are {\bf T}-dual to each other, the results are not affected.

%Before we invoke the folding trick, we need to note one important caveat here. In the usual treatment of boundary CFT, for example in , the field is quantized on the real axis. As emphasized in Sec.~\ref{sec:bosonic_conformal_interface}, the gluing condition becomes an operator identity of creation and annihilation operators, which is valid \emph{only} when acting on the conformal boundary states.

We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
The folding sends $\phi^2(t)\rightarrow\phi^2(-t)$ for $t<0$, and the $\partial_t \phi^2$ term changes sign, we therefore have 
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\begin{pmatrix}
\partial_+\phi^1\\
-\partial_+\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
-\partial_-\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}
For convenience, we shift $\phi^2\rightarrow-\phi^2$ by a sign. This amounts to reparameterize the S-matrix and exchange the two sectors of $O(2)$ group. But this will not change our conclusion in the main text. 
\todo[inline]{Check the parameterization} 
Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

@@

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \quad \implies \quad ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
\end{aligned}
\end{equation}
and the conformal boundary state reads
\begin{equation}\begin{aligned}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not repeat the calculation here. Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in a similar parameter $\lambda$ and boundary state. We omit the expression here because the main text does not use it.

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle\lambda_2|e^{-\pi H}|\lambda_1\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
\end{aligned}\end{equation}
To that end, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 = \sum_{S_1 } g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}
\end{equation}
In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{\lambda_1} }g_{\,\!_{\lambda_2} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{equation}
The integral is a constant, thus the winding mode will contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution is negligible in the large $\beta$ limit.

For the case $\lambda_1\neq\lambda_2$, the partition function will acquire non-zero contribution from the least common divisor of $(n_1,m_1)$ and $(n_2,m_2)$. The same conclusion still holds in the limit $\beta\rightarrow\infty$.

>>>>

\subsection{Gluing Condition for the Winding Modes}
\label{app_sub:compact_gluing_boundary}

Here we solve the boundary state on the $t = 0$ slice. Our actual boundary state used in the text corresponds to the $x = 0$ slice. There is a $x \rightarrow t$ exchange in the convention here. However, that amounts to the change of $\theta \rightarrow \frac{\pi}{2} - \theta$ in the $S$ matrix argument.

\todo[inline]{Mao: this is not a T-dual transformation, it is DN -> ND. }
We recall that the gluing condition is written as
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app}
\begin{pmatrix}
\partial_+\phi^1\\
\partial_-\phi^2
\end{pmatrix}
=S(\theta)
\begin{pmatrix}
\partial_-\phi^1\\
\partial_+\phi^2
\end{pmatrix}
\end{aligned}
\end{equation}

Upon mode expanding $\phi^{1,2}$ in the holomorphic coordinates as in Eq.~\eqref{eq:boson-mode-exp}, we have
\begin{equation}
\begin{aligned}
\label{eq:def_S_in_app_2}
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
\bar{a}_n^1\bar{z}^{-n}\\
\bar{a}_n^2\bar{z}^{-n}
\end{pmatrix}
=S(\theta)
\sum_{n\in\mathbb{Z}}
\begin{pmatrix}
a_n^1{z}^{-n}\\
a_n^2{z}^{-n}
\end{pmatrix}
\end{aligned}
\end{equation}
As explained above, the boundary condition is imposed at $t=0$, where $\bar{z}=z^{-1}$, therefore we have
\begin{equation}\begin{aligned}
a^i_n-(S^{-1}_{ij})\bar{a}^j_{-n}=0
\end{aligned}\end{equation}
The solution of the $n \ne 0$ constraints is exactly the boundary state in Eq.~\eqref{eq:bd_state}.

@@

We specialize to $S = S_1$ to solve the $ n = 0$ constraint. We introduce the compactification lattice and its dual\cite{affleck_quantum_2001,oshikawa_boundary_2010}
\begin{equation}
\label{eq:lattice}
\vec{M} = (m_1 2 \pi R_1, m_2 2\pi  R_2)^\top, \quad  \vec{M}^* = (\frac{n_1}{R_1}, \frac{n_2}{R_2})^\top
\end{equation}
to rewrite the zero mode part as 
\begin{equation}
  a_0^i - S^{-1} _{ij} \bar{a}_{0}^j = 0 \,\, \implies \,\, ( \vec{M} + \frac{1}{g}\vec{M}^* ) = S_1 ( -\vec{M} + \frac{1}{g}\vec{M}^* )
\end{equation}
which is basically the multi-component boson winding constraints given in \onlinecite{affleck_quantum_2001,oshikawa_boundary_2010}. The solution gives the interface parameter $\lambda$
\begin{equation}
\begin{aligned}
\label{eq:S_1_constraint}
\lambda = \tan\theta=\frac{n_2R_1}{n_1R_2}=-\frac{m_1R_1}{m_2R_2}
\end{aligned}
\end{equation}
and the conformal boundary state
\begin{equation}\begin{aligned}
\label{eq:S1bd-state}
g_{S_1}\sum_{S_1}e^{in_1\phi_0-im_1\bar{\phi}_0}|n_1,m_1\rangle|n_2,m_2\rangle
\end{aligned}\end{equation}
where $\sum_{S_1}$ is the summation consistent with the constraint in Eq.~\eqref{eq:S_1_constraint}. The g-factor can only be determined by Cardy condition\cite{cardy_boundary_2004}. Since it is not important for what follows, we shall not include the calculation here.

Since $S = S_2$ is effectively $S_1$ on the dual boson, we can expect that it will end up in the same expression as in Eq.~\eqref{eq:S1bd-state}, but with a different constraints on the winding number
\begin{equation}
\vec{M} = \frac{\cot \theta}{g} 
\begin{bmatrix}
0 & -1\\
1 & 0 \\                                
\end{bmatrix}
\vec{M}^*
\end{equation}

\subsection{Winding Mode Contribution to the Partition Function}
\label{app_sub:winding_contribution}
We now calculate the winding mode part of the partition function as shown in Fig.~\ref{fig:fig_lambda_1_lambda_2}
\begin{equation}\begin{aligned}
Z=\langle S_j( \theta_2 )|e^{-\pi H}|S_i(\theta_1 )\rangle\qquad H=\frac{2\pi}{\beta}(L_0+\bar{L}_0)
\end{aligned}\end{equation}
With boundary state, we can simply replace $L_0$($\bar{L}_0$) with $a_0$($\bar{a}_0$).

For the amplitude between the same boundary states $\lambda_1=\lambda_2$, we have the winding mode contribution as
\begin{equation}
\begin{aligned}
\label{eq:Z0}
Z_0 \le  \sum_{S_i} g_{\,\!_{S_i} }g_{\,\!_{S_j} } \exp\Big\{- \frac{4\pi}{\beta} 2 \pi g ( \frac{n_1}{ 4 \pi R_1 g} + \frac{m_1 R_1 }{ 2} )^2 \Big\}
\end{aligned}
\end{equation}
where the equality only is only taken when the two boundary states are identical.

In the limit $\beta\rightarrow\infty$, Eq.~\eqref{eq:Z0} can be approximated by a simple two dimensional integral
\begin{equation}\begin{aligned}
Z_0\approx g_{\,\!_{S_i} }g_{\,\!_{S_j} }\beta\int dxdy\exp\Big\{-8 \pi^2 g ( \frac{x}{ 4 \pi R_1 g} + \frac{y R_1 }{ 2} )^2 \Big\}
\end{aligned}\end{equation}
The winding mode thus can contribute at most a $\ln\beta$ term to the free energy. Compared to the result in App.~\ref{app:gnd_dn_lambda}-\ref{app:lambda_12}, we conclude that the winding mode contribution will not present in the leading order of large $\beta$ limit.

### 2017-05-23 conclusion.tex
[draft] App. G checked. PDN data added. Whole paper 1st pass.

In this paper, we analyze a class of boson conformal interfaces by computing the fidelity and Loschmidt echo.

We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ while `DN' and $P$ belongs to $S_2$. A harmonic chain model allows us to realize part of these boundary conditions, including the partially-transmitive ones, on a concrete setting.

The study of the Loschmidt echo are a generalization of the conventional ``cut-and-join" protocol. Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient. Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices. While the exponent will depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$.

These two features are tested in three typical processes in the numerical calculation. After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error. Although irrelevant to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement, providing more confidence about the analytic results.

We proposed that the Loschmidt echo exponent in principle should be realizable in connecting two quantum wire with an X-ray type experiment.

>>>>

In this paper, we analyze a class of boson conformal interfaces by computing the Loschmidt echo and the bipartite fidelity.

We begin by classifying the boundary states by two types of $S$ matrices, where the conventional `DD', `NN' boundary conditions belong to $S_1$ and  `DN' and P belongs to $S_2$. A harmonic chain model allows us to realize part of these partially-transmitive boundary conditions a concrete lattice setting.

The study of the Loschmidt echo is a generalization of the conventional ``cut-and-join" protocol. Its power law decay exponent is related to the bcc operator scaling dimension that can depend on the tune-able transmission coefficient. Analytic computation shows that the exponent is $\frac{1}{4}$ when the change of boundary condition is made between different types of $S$ matrices and depend on $\theta$ (scattering angle in the $S$ matrix) as a quadratic relation when the change is made between the same types of $S$ matrices of different $\theta$s.

These two features are tested in three typical processes in the numerical calculation of the harmonic chains. After using suitable regulators for the zero-mode problem, the numerical results agree with the analytic calculation within error. Although tangential to the non-equilibrium dynamics, the fidelity calculation is used as a diagnostic tool and shows better agreement of the exponent, providing more confidence about our analytic results.

We proposed that the Loschmidt echo exponent in principle should be detectable in an X-ray edge singulrity type experiment on quantum wires systems.
